\documentclass[letterpaper,10pt]{article}

\usepackage[pdftex]{hyperref}
\usepackage{multicol}
\usepackage{geometry}
\usepackage{titlesec}

\geometry{letterpaper, portrait, margin=.75in}

\setlength\parindent{0pt}
\hyphenpenalty=10000

\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

% standard line break in content paragraph
\newcommand{\lb}{\vspace{4pt} \\}

% TODO: consolidate these resumecols commands
\newenvironment{resumecols1}[1]
{
    \vspace{.1cm}
    \begin{minipage}[t]{.21\linewidth}
        \begin{flushright}
            \textsc{#1}
        \end{flushright}
    \end{minipage}
    \hspace{.005\linewidth}
    \begin{minipage}[t]{.77\linewidth}
}
{
    \end{minipage}
    \vspace{.1cm}
}

\newenvironment{resumecols2}[2]
{
    \vspace{.1cm}
    \begin{minipage}[t]{.21\linewidth}
        \begin{flushright}
            \textsc{#1} \\
            \small{#2}
        \end{flushright}
    \end{minipage}
    \hspace{.005\linewidth}
    \begin{minipage}[t]{.77\linewidth}
}
{
    \end{minipage}
    \vspace{.1cm}
}

\newenvironment{resumecols}[4]
{
    \vspace{.1cm}
    \begin{minipage}[t]{.21\linewidth}
        \begin{flushright}
            \href{#2}{\textsc{#1}} \\
            \small{\textit{#3}} \\
            \small{#4}
        \end{flushright}
    \end{minipage}
    \hspace{.005\linewidth}
    \begin{minipage}[t]{.77\linewidth}
}
{
    \end{minipage}
    \vspace{.1cm}
}

\begin{document}

\thispagestyle{empty}

%%%%%%%%%%%%%%
%%% HEADER %%%
%%%%%%%%%%%%%%
\begin{flushright}
    \textbf{\Large{Dominic Zirbel}} \\
    \href{mailto:dominiczirbel@gmail.com}{dominiczirbel@gmail.com} \\
    \href{https://github.com/dzirbel}{github.com/dzirbel} \\
    412 204 7462
\end{flushright}

%%%%%%%%%%%%%%%%%%
%%% EXPERIENCE %%%
%%%%%%%%%%%%%%%%%%
\section{Experience}

\begin{resumecols}{Thumbtack}{https://www.thumbtack.com/about}{Senior Software Engineer}{June 2018 - Present}
    Worked on the Growth and Platform teams as an Android engineer. I built features and ran A/B tests on native Android apps and backend in Go/PHP/Python. As part of the small Mobile Infrastructure team I managed app architecture, CI/release pipelines, and developer productivity for the entire Android team. I conceived, planned, and drove adoption of new technologies including Jetpack Compose, Room, and Kotlin Coroutines.
\end{resumecols}

\begin{resumecols}{Kotify}{https://github.com/dzirbel/kotify}{Solo Project}{2019 - Present}
    A work-in-progress side project providing a third party desktop client for Spotify via its \href{https://developer.spotify.com/documentation/web-api/}{web API} which I created and developed individually for enjoyment and practice. Built in Kotlin with \href{https://www.jetbrains.com/lp/compose-mpp/}{JetBrain's multiplatform bindings} for \href{https://developer.android.com/jetpack/compose}{Jetpack Compose}, the project aims to add new features on top of Spotify's platform to improve personal library organization.
\end{resumecols}

\begin{resumecols}{Thumbtack}{https://www.thumbtack.com/about}{Software Engineer Intern}{Summer 2017}
    Rebuilt the login flow in the Thumbtack customer Android app from the ground up. I added account creation and Facebook login, modernized the UI, and ran A/B tests.
\end{resumecols}

\begin{resumecols}{Imaging Systems Technology}{http://www.teamist.com}{Android Intern}{Summer 2016}
    Developed an Android tablet app to monitor and control a manufacturing process. The app received live data via Bluetooth, calculated aggregates, displayed realtime graphs, and kept logs of past runs. I focused on handling large amounts of data in an extensible way and presenting the data in ways that facilitated the team's decision making.
\end{resumecols}

\begin{resumecols}{MetabolismFun}{https://github.com/dzirbel/metabolism-fun}{Full-Stack Web Engineer}{July 2013 - Jan 2015}
    Created the online educational game MetabolismFun (\href{https://github.com/dzirbel/metabolism-fun}{\underline{GitHub source}}) with Dr.\ Neocles Leontis at BGSU to teach metabolic pathways to college students in an engaging, interactive way. I was responsible for programming, design, and deployment.
\end{resumecols}

\begin{resumecols}{Agile Oasis Technologies}{http://agileoasis.com}{Web Developer Intern}{Summer 2015, 2013}
    Designed and built a variety of contracted websites, and including a social network Project Qi connecting users to non-profitss. I worked closely with the clients to craft the experiences they had in mind.
\end{resumecols}

\begin{resumecols}{Personal Robotics}{https://personalrobotics.cs.washington.edu}{Research Intern}{Summer 2012}
    Designed an Android tablet app for in-house use with the humanoid robot HERB. The app provided a simple interface for normally difficult tasks such as adjusting motor position, displaying sensor output, or sending a direct command.
\end{resumecols}

%%%%%%%%%%%%%%
%%% SKILLS %%%
%%%%%%%%%%%%%%
\section{Skills}

\begin{resumecols1}{Native Android Engineering}
    Comprehensive knowledge of the native Java API, including Kotlin, Gradle, Compose \\
    Worked with industry standards, mature codebases, and large-scale deployments
\end{resumecols1}

\begin{resumecols1}{Programming}
    Koltin/Java, Go, Python: solid foundation in the style and uses of these languages \\
    Web development: GraphQL, Go, PHP, SQL, JavaScript, and HTML/CSS \\
    Linux: daily usage of top-level components (CLI, Bash scripting, Git) \\
    Contributed to open source projects including \href{https://github.com/detekt/detekt/issues?q=author\%3Adzirbel}{\underline{detekt}} and \href{https://github.com/willowtreeapps/assertk/issues?q=author\%3Adzirbel}{\underline{assertk}}
\end{resumecols1}

\begin{resumecols1}{Mathematics}
    Strong academic core with a focus on Analysis, Combinatorics, and Abstract Algebra \\
    Analytical thinking, problem solving, and abstract reasoning
\end{resumecols1}

%%%%%%%%%%%%%%%%%
%%% EDUCATION %%%
%%%%%%%%%%%%%%%%%
\section{Education}

\begin{resumecols2}{Carnegie Mellon University}{Class of 2018}
    BS in Mathematical Sciences with an additional major in Computer Science
    \lb
    Cumulative GPA: 3.41
\end{resumecols2}

\end{document}
