\documentclass[letterpaper,10pt]{article}

\usepackage[pdftex]{hyperref}
\usepackage{geometry}

\geometry{letterpaper, portrait, margin=1.5in}

\setlength\parindent{0pt}
\hyphenpenalty=10000

% standard line break in content paragraph
\newcommand{\lb}{\vspace{14pt} \\}

\begin{document}

\thispagestyle{empty}

%%%%%%%%%%%%%%
%%% HEADER %%%
%%%%%%%%%%%%%%
\begin{flushright}
    \textbf{\Large{Dominic Zirbel}} \\
    \href{mailto:dominiczirbel@gmail.com}{dominiczirbel@gmail.com} \\
    \href{https://github.com/djynth}{github.com/djynth} \\
    412 204 7462
\end{flushright}

\vspace{36pt}

Dear HCII Hiring Team,
\lb
I am writing to express my interest in the Android Developer on-campus job offered by HCII. I'm a Senior double majoring in Mathematics and Computer Science at CMU and I'm looking for on-campus opportunities this school year. I have multiple summers worth of experience working with Android including all the areas you are looking for: networking, some backend experience, data visualization, and more. I think I would be an excellent fit for the position.
\lb
I have been working with Android since high school; in fact, my first Android experience was during the summer of 2012 when I interned at the Personal Robotics research lab right here at CMU. I built an Android app for tablets to monitor and control the robot HERB which was under development by the lab. I've continued working in Android the last two summers, most recently at an internship with the San Francisco startup Thumbtack. At Thumbtack I rewrote the login process for new and returning users, including signing in, creating an account, logging in with Facebook, account recovery with email, and more. I used the native Java SDK (as well as picking up some Kotlin) and dealt with the application from the network layer to the user interface and everything in between. I learned industry-standard best practices and had to familiarize myself with their codebase quickly. I am able to work independently, communicate technical issues well, and develop new features rapidly.
\vspace{14pt}
Please see my attached resume for a more complete description of my background and skills. Feel free to follow up via Handshake or email me directly at \texttt{dominiczirbel@gmail.com} or \texttt{dzirbel@andrew.cmu.edu}. Thank you for considering my application and I will look forward to hearing back from you!
\lb
Sincerely, \\
Dominic Zirbel

\end{document}
