\documentclass[letterpaper,10pt]{article}

\usepackage[pdftex]{hyperref}
\usepackage{geometry}

\geometry{letterpaper, portrait, margin=1.5in}

\setlength\parindent{0pt}
\hyphenpenalty=10000

% standard line break in content paragraph
\newcommand{\lb}{\vspace{14pt} \\}

\begin{document}

\thispagestyle{empty}

%%%%%%%%%%%%%%
%%% HEADER %%%
%%%%%%%%%%%%%%
\begin{flushright}
    \textbf{\Large{Dominic Zirbel}} \\
    \href{mailto:dominiczirbel@gmail.com}{dominiczirbel@gmail.com} \\
    \href{https://github.com/djynth}{github.com/djynth} \\
    412 204 7462
\end{flushright}

\vspace{36pt}

Dear Folsom hiring team,
\lb
I am writing to express my interest in the Software Engineer position at Folsom Labs. As a double major in Mathematics and Computer Science at Carnegie Mellon University with excellent internship experience, I am very well suited to take on the challenges faced by Folsom. I am looking for a full-time role after my graduation in May 2018, and I believe Folsom offers the excitement of a startup and room to grow that I am interested in.
\lb
Folsom is dealing with interesting problems on both the technical and the user interface levels, and my combination of a strong theoretical background and practical experience allows me to handle the stack at all levels. My coursework at Carnegie Mellon, especially as a math double major, emphasizes abstract ideas and analytical thinking. With a background including parallel data structures, graph theory, and machine learning, I am capable of analyzing and implementing the algorithms required by next the generation technologies being developed by Folsom. Moreover, my internship experience at Thumbtack and others has given me the practical tools and soft skills to be effective in a team environment. Many of these skills, such as technical communication and attention to detail, are universally valuable in software engineering and I hope to bring them to Folsom.
\lb
For these reasons and more I am confident I could be a great asset to your team at Folsom Labs. Please see my attached resume for a more complete description of my background and skills and feel free to contact me at \texttt{dominiczirbel@gmail.com} or (412) 204-7462. Thank you for your consideration, I will be hoping to hear from you in the coming weeks.
\lb
Sincerely, \\
Dominic Zirbel

\end{document}
