\documentclass[letterpaper,10pt]{article}

\usepackage[pdftex]{hyperref}
\usepackage{geometry}

\geometry{letterpaper, portrait, margin=1.5in}

\setlength\parindent{0pt}
\hyphenpenalty=10000

% standard line break in content paragraph
\newcommand{\lb}{\vspace{14pt} \\}

\begin{document}

\thispagestyle{empty}

%%%%%%%%%%%%%%
%%% HEADER %%%
%%%%%%%%%%%%%%
\begin{flushright}
    \textbf{\Large{Dominic Zirbel}} \\
    \href{mailto:dominiczirbel@gmail.com}{dominiczirbel@gmail.com} \\
    \href{https://github.com/djynth}{github.com/djynth} \\
    412 204 7462
\end{flushright}

\vspace{36pt}

Dear Riot Games Hiring Team,
\lb
I am writing to express my interest in a position as a Software Engineer at Riot Games. As a double major in Mathematics and Computer Science at Carnegie Mellon University and an avid League of Legends player it would be an incredible experience to contribute to a game I love so much. I am looking for a full-time role after my graduation in May 2018 and between the culture, mission, and passion at Riot there is no place I would rather work.
\lb
Like so many young programmers, my interest in coding began as a desire to create games. I began in middle school by picking up a Java textbook and was instantly hooked. As I learned enough to start building practical applications I realized what I enjoyed most was creating an experience that was polished to an extreme: intuitive, pleasant to use, powerful. Dialing back my ambitions from a fully-featured game, I strove to make an application that I would actively enjoy to use, which eventually took the form of a half-tool, half-game simulation of John Conway's Game of Life (the code, while outdated, can be found \href{https://github.com/djynth/Game-of-Life}{\texttt{here}} on GitHub). In addition to the valuable technical experience of maintaining a project over the course of multiple years, the experience taught me what I enjoy most about software development: building a product that I myself would love to use.
\lb
Great things can be done when passion and skill come together. My coursework at Carnegie Mellon - including parallel data structures, graph theory, and machine learning - has given me the versatility to handle problems from across the stack. Complemented with soft skills from my internship experience, I am eager to take on the challenges of contemporary software development. I pride myself on my ability to learn quickly and independently and I would love to bring both my skillset and zeal to Riot.
\lb
Please see my attached resume for a more complete description of my background and skills and feel free to contact me at \texttt{dominiczirbel@gmail.com} or (412) 204-7462. Thank you for your consideration, I will be hoping to hear from you in the coming weeks.
\lb
Sincerely, \\
Dominic Zirbel

\end{document}
