\documentclass[letterpaper,10pt]{article}

\usepackage[pdftex]{hyperref}
\usepackage{geometry}

\geometry{letterpaper, portrait, margin=1.5in}

\setlength\parindent{0pt}
\hyphenpenalty=10000

% standard line break in content paragraph
\newcommand{\lb}{\vspace{14pt} \\}

\begin{document}

\thispagestyle{empty}

%%%%%%%%%%%%%%
%%% HEADER %%%
%%%%%%%%%%%%%%
\begin{flushright}
    \textbf{\Large{Dominic Zirbel}} \\
    \href{mailto:dominiczirbel@gmail.com}{dominiczirbel@gmail.com} \\
    \href{https://github.com/djynth}{github.com/djynth} \\
    412 204 7462
\end{flushright}

\vspace{36pt}

Dear Mr. Cramer and Mr. Maschke,
\lb
I am writing to express my interest in the Java / Web Programmer position at Sapio Sciences. As a double major in Mathematics and Computer Science at Carnegie Mellon University and with ample experience in both Java and full-stack web engineering, I am an excellent candidate for the position. I am looking for a full-time role after my graduation in May 2018, and I believe Sapio Sciences offers the combination of a focused work environment and professional team that I am interested in.
\lb
Working in Java has been core to my professional and personal background since the beginning of my interest in programming. Java was my very first programming language; I taught myself in middle school from a spare textbook as there was no longer enough interest to offer the class. I used Java exclusively throughout high school in side projects, culminating in a half-game, half-tool simulation of John Conway's Game of Life which can still be found on my GitHub page. I have continued using Java professionally with my work on Android including at my most recent internship at Thumbtack. At Thumbtack, I worked on the login process for users in their Android app, gaining both technical skills and experience working in a professional software development team. Many of these skills, such as technical communication and attention to detail, are universally valuable in software engineering and I hope to bring them to Sapio Sciences.
\lb
My courses at Carnegie Mellon have also prepared me extraordinarily well for a role in software engineering. My coursework, especially as a math double major, emphasizes abstract ideas and analytical thinking. Sapio Sciences faces modern challenges in data analytics, and I am capable of implementing appropriate solutions with a background including parallel data structures, graph theory, advanced algorithms, and machine learning. In addition to theory, I made a point of focusing on practical software engineering. For example, I took a course called ``Principles of Software Construction'' which taught best practices for managing large, mature codebases in Java. My studies have supplemented my experience and made me a competent programmer eager to take on the challenges of contemporary software development.
\lb
For these reasons and more I know I could be a great asset to your team at Sapio Sciences. Please see my attached resume for a more complete description of my background and skills and feel free to contact me at \texttt{dominiczirbel@gmail.com} or (412) 204-7462. Thank you for your consideration, I will be hoping to hear from you in the coming weeks.
\lb
Sincerely, \\
Dominic Zirbel

\end{document}
